Verifying Demonstrations

### 2017-09-30 protocol.tex
Edits temporal eligibility and moves up linkability

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
proofs to the blockchain as soon as possible after they have participated in the 
protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
block in the blockchain.
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

@@

\subsection{Location proofs and spatial eligibility}

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

>>>>

With the above properties, \cref{CreatedBeforeEnd} is straight-forward: Alice 
and Bob simply commit their proofs to the blockchain as soon as possible after 
they have participated in the protest.
Thus we can infer that a proof (or proof share) was created at the latest when 
it was committed.
For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
existing block in the blockchain.
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.proof
        {share}
        [.{share} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {share}
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.proof
      {share}
      [.{share} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {share}
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (share), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

\subsubsection{Location proofs and spatial eligibility}

@@
